Software Ticket Quality

### 2017-11-20 proposal/mprop.tex
Add skeleton for paper and bib entry to fuzzy code search to link code fragments in discussions to source code paper

>>>>

\textbf{Using fuzzy code search to link code fragments in discussions to source code}\cite{bettenburg2012using}:
\begin{itemize}
  \item \textbf{What were the goals?}
    The main goal of the paper is to find an approach that improves on
    previous methods to link source code fragments in discussions to source code.
    These previous methods were mainly based on information retrieval or 
    change log analysis.
  \item \textbf{What was the method?}
  \item \textbf{What did they learn?}
  \item \textbf{Relevance to our work}:
\end{itemize}
